\vspace{-0.5cm}The X-shooter GTO sample of GRB afterglow and host Galaxy spectra

### 2016-10-15 document/XSGRB_sample.tex
More notes on individual bursts

\newcommand{\griz}{$g' r' i' z'$}
\newcommand{\JHK}{$JHK_{\rm{s}}$}
\newcommand{\gK}{$g' r' i' z' JHK_{\rm{s}}$}
\newcommand{\Msun}{$M_\odot$}
\newcommand{\lya}{Ly$\alpha$} 
\newcommand{\lyb}{Ly$\beta$} 
\newcommand{\hb}{H$\beta$} 
\newcommand{\ha}{H$\alpha$} 
\newcommand{\hg}{H$\gamma$} 
\newcommand{\hi}{\ion{H}{1}} 
\newcommand{\hei}{[\ion{He}{1}]} 
\newcommand{\oi}{[\ion{O}{1}]} 
\newcommand{\sii}{[\ion{S}{2}]} 
\newcommand{\siii}{[\ion{S}{3}]} 
\newcommand{\oii}{[\ion{O}{2}]$\lambda$3727} 
\newcommand{\oiii}{[\ion{O}{3}]$\lambda$5007}
\newcommand{\nii}{[\ion{N}{2}]} 
\newcommand{\neiii}{[\ion{Ne}{3}]} 
\newcommand{\feii}{\ion{Fe}{2}} 
\newcommand{\civ}{\ion{C}{4}} 
\newcommand{\cii}{\ion{C}{2}}
\newcommand{\mgi}{\ion{Mg}{1}} 
\newcommand{\mgii}{\ion{Mg}{2}} 
\newcommand{\ali}{\ion{Al}{1}} 
\newcommand{\alii}{\ion{Al}{2}} 
\newcommand{\aliii}{\ion{Al}{3}} 
\newcommand{\SIii}{\ion{Si}{2}} 
\newcommand{\znii}{\ion{Zn}{2}} 
\newcommand{\crii}{\ion{Cr}{2}} 
\newcommand{\mnii}{\ion{Mn}{2}} 
\newcommand{\tiii}{\ion{Ti}{2}} 
\newcommand{\caii}{\ion{Ca}{2}}

@@

@@

	\newpage
	\appendix
	\section{Notes on Individual objects}

@@

@@

	\subsection{GRB160804A (z = 0.736)}
	The data presented here also formed the basis of GCN \#
	19773\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/19773.gcn3}} and is not
	published elsewhere. Observations started 22.37 hours after the BAT trigger and
	lasted for 2.4ks. The afterglow continuum is detected across the entire
	spectral coverage of X-shooter and absorption lines from \mgi, \mgii, \feii and
	\alii~are found at $z = 0.736$. At the same redshift, emission lines from \oii,
	\oiii, \ha, \hb, \hg, \nii, \sii, \siii are found. A second epoch, lasting
	3.6ks, is obtained after the afterglow has faded, confirming the emission line
	detections.

>>>>

\newcommand{\griz}{$g' r' i' z'$}
\newcommand{\JHK}{$JHK_{\rm{s}}$}
\newcommand{\gK}{$g' r' i' z' JHK_{\rm{s}}$}
\newcommand{\Msun}{$M_\odot$}
\newcommand{\lya}{Ly$\alpha$} 
\newcommand{\lyb}{Ly$\beta$} 
\newcommand{\hb}{H$\beta$} 
\newcommand{\ha}{H$\alpha$} 
\newcommand{\hg}{H$\gamma$} 
\newcommand{\hi}{\ion{H}{1}} 
\newcommand{\hei}{[\ion{He}{1}]} 
\newcommand{\oi}{[\ion{O}{1}]} 
\newcommand{\sii}{[\ion{S}{2}]} 
\newcommand{\siii}{[\ion{S}{3}]} 
\newcommand{\oii}{[\ion{O}{2}]$\lambda$3727} 
\newcommand{\oiii}{[\ion{O}{3}]$\lambda$5007}
\newcommand{\nii}{[\ion{N}{2}]} 
\newcommand{\neiii}{[\ion{Ne}{3}]} 
\newcommand{\NIii}{[\ion{Ni}{2}]} 
\newcommand{\feii}{\ion{Fe}{2}} 
\newcommand{\civ}{\ion{C}{4}} 
\newcommand{\cii}{\ion{C}{2}}
\newcommand{\mgi}{\ion{Mg}{1}} 
\newcommand{\mgii}{\ion{Mg}{2}} 
\newcommand{\ali}{\ion{Al}{1}} 
\newcommand{\alii}{\ion{Al}{2}} 
\newcommand{\aliii}{\ion{Al}{3}} 
\newcommand{\SIii}{\ion{Si}{2}} 
\newcommand{\SIiv}{\ion{Si}{4}} 
\newcommand{\znii}{\ion{Zn}{2}} 
\newcommand{\crii}{\ion{Cr}{2}} 
\newcommand{\mnii}{\ion{Mn}{2}} 
\newcommand{\tiii}{\ion{Ti}{2}} 
\newcommand{\caii}{\ion{Ca}{2}}

\usepackage{todonotes}

@@

	A significant fraction of the bursts presented here \todo[inline]{Insert exact number} have already had their hosts investigated in \citet{Kruhler2015}, for which extractions of the hosts exist. The focus of the data presented here are on the afterglows themselves and in the absence of a clear afterglow, the host. We will not, however, investigate the hosts.

@@

	\newpage
	\appendix

	\section{Notes on Individual objects}

@@

	\subsection{GRB120714B (z = 0.398)}
	The data presented here also formed the basis of GCN \#
	13477\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/13477.gcn3}}, but is not
	published elsewhere. Observations of this burst started 7.8 hours after the GRB
	trigger, lasting 4.8 ks. A continuum is visible across the entire spectral
	coverage of X-shooter, with both emission lines from  \oii, \hb, \oiii~and \ha,
	as well as absorption from \mgii~detected at $z = 0.398$, securely setting it
	as the redshift of the GRB.

	\subsection{GRB120716A (z = 2.486)}
	The data presented here also formed the basis of GCN \#
	13494\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/13494.gcn3}}, but is not
	published elsewhere. Despite observations starting 62 hours after the
	\textit{Swift} trigger and lasting 3.6 ks, a bright afterglow is clearly seen,
	along with a plethora of absorption features. Absorption of \lya-photons in the
	host leaves a broad trough, from which the Lyman alpha forest is visible
	bluewards, all the way down to the Lyman limit. Metal absorption lines from
	\cii, \SIii, \oi, \feii, \civ, \SIiv, including fine structure transitions
	identified as \cii$^*$, \SIii$^*$, \feii$^*$ and metastable \NIii~lines are all
	detected at $z = 2.486$

	\subsection{GRB120722A (z = 0.959)}
	The data presented here also formed the basis of GCN \#
	13507\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/13507.gcn3}}, but is not
	published elsewhere. On 4.8 ks integration time, starting 10 hours after the
	burst trigger, the simultaneous detection of absorption features belonging to
	\mgii~and \feii~superposed on a blue continuum, and emission lines from \oii,
	\hg, \hb, \oiii~and \ha, all at $z = 0.959$, confidently sets it as the
	redshift of the GRB.

@@

	\subsection{GRB160804A (z = 0.736)}
	The data presented here also formed the basis of GCN \#
	19773\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/19773.gcn3}} and is not
	published elsewhere. Observations started 22.37 hours after the BAT trigger and
	lasted for 2.4ks. The afterglow continuum is detected across the entire
	spectral coverage of X-shooter and absorption lines from \mgi, \mgii, \feii~and
	\alii~are found at $z = 0.736$. At the same redshift, emission lines from \oii,
	\oiii, \ha, \hb, \hg, \nii, \sii, \siii~are found. A second epoch, lasting
	3.6ks, is obtained after the afterglow has faded, confirming the emission line
	detections.
